Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Shanghai version \YellowPaperVersionNumber}}

### 2024-04-23 Paper.tex
eip-6049
shanghai

\title[Ethereum: A Secure Decentralised Generalised Transaction Ledger\\ \smaller \textbf{{Paris version}}]{Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Paris version \YellowPaperVersionNumber}}}
\author{
    Dr. Gavin Wood\\
    Founder, Ethereum \& Parity\\
    gavin@parity.io
}
\begin{document}

@@

There are many versions of Ethereum, as the protocol has undergone a number of updates.
These updates can be specified to occur:
\begin{itemize}
  \item at a particular block number in the case of pre-\textit{Paris} updates,
  \item after reaching a \textit{terminal total difficulty} in the case of the \textit{Paris} update, or
  \item at a particular block timestamp in the case of post-\textit{Paris} updates.
\end{itemize}
This document describes the \textit{Paris} version.

In order to follow back the history of a path, one must reference multiple versions of this document.
Here are the block numbers of protocol updates on the Ethereum main network:\footnote{Note that while the Paris fork activated at block 15,537,394, the trigger was not the block number, but rather reaching a specified \textit{total difficulty}. The trigger for the \textit{Paris} hard fork is discussed in greater detail in section \ref{ch:pos_transition}.}
\par
\begin{center}
\begin{tabular}{lr}
\toprule
Name & First Block Number \\
\midrule
$F_{\mathrm{Homestead}}$         &  1150000 \\
$F_{\mathrm{Tangerine Whistle}}$ &  2463000 \\
$F_{\mathrm{Spurious Dragon}}$   &  2675000 \\
$F_{\mathrm{Byzantium}}$         &  4370000 \\
$F_{\mathrm{Constantinople}}$    &  7280000 \\
$F_{\mathrm{Petersburg}}$        &  7280000 \\
$F_{\mathrm{Istanbul}}$          &  9069000 \\
$F_{\mathrm{Muir Glacier}}$      &  9200000 \\
$F_{\mathrm{Berlin}}$            & 12244000 \\
$F_{\mathrm{London}}$            & 12965000 \\
$F_{\mathrm{Arrow Glacier}}$     & 13773000 \\
$F_{\mathrm{Gray Glacier}}$      & 15050000 \\
$F_{\mathrm{Paris}}$             & 15537394 \\
\bottomrule
\end{tabular}
\end{center}
\par

@@

@@

\linkdest{selfdestruct}{}0xff & {\small SELFDESTRUCT} & 1 & 0 & Halt execution and register account for later deletion. \\

>>>>

\title[Ethereum: A Secure Decentralised Generalised Transaction Ledger\\ \smaller \textbf{{Shanghai version}}]{Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Shanghai version \YellowPaperVersionNumber}}}
\author{
    Dr. Gavin Wood\\
    Founder, Ethereum \& Parity\\
    gavin@parity.io
}
\begin{document}

@@

There are many versions of Ethereum, as the protocol has undergone a number of updates.
These updates can be specified to occur:
\begin{itemize}
  \item at a particular block number in the case of pre-\textit{Paris} updates,
  \item after reaching a \textit{terminal total difficulty} in the case of the \textit{Paris} update, or
  \item at a particular block timestamp in the case of post-\textit{Paris} updates.
\end{itemize}
This document describes the \textit{Shanghai} version.

In order to follow back the history of a path, one must reference multiple versions of this document.
Here are the block numbers of protocol updates on the Ethereum main network:\footnote{Note that while the Paris, Shanghai, and every upcoming forks activated at a given block number (e.g. 15,537,394 for Paris), the trigger was not the block number, but rather reaching a specified \textit{timestamp} (or \textit{total difficulty} for Paris). The trigger for the \textit{Paris} and subsequent hard fork are discussed in greater detail in section \ref{ch:pos_transition}.}
\par
\begin{center}
\begin{tabular}{lr}
\toprule
Name & First Block Number \\
\midrule
$F_{\mathrm{Homestead}}$         &  1150000 \\
$F_{\mathrm{Tangerine Whistle}}$ &  2463000 \\
$F_{\mathrm{Spurious Dragon}}$   &  2675000 \\
$F_{\mathrm{Byzantium}}$         &  4370000 \\
$F_{\mathrm{Constantinople}}$    &  7280000 \\
$F_{\mathrm{Petersburg}}$        &  7280000 \\
$F_{\mathrm{Istanbul}}$          &  9069000 \\
$F_{\mathrm{Muir Glacier}}$      &  9200000 \\
$F_{\mathrm{Berlin}}$            & 12244000 \\
$F_{\mathrm{London}}$            & 12965000 \\
$F_{\mathrm{Arrow Glacier}}$     & 13773000 \\
$F_{\mathrm{Gray Glacier}}$      & 15050000 \\
$F_{\mathrm{Paris}}$             & 15537394 \\
$F_{\mathrm{Shanghai}}$          & 17034870 \\
\bottomrule
\end{tabular}
\end{center}
\par

@@

\subsection{Post-Paris Updates}
Because the Beacon Chain generate a new slot every 12 seconds, post-\textit{Paris} updates can be scheduled to occur at a specific timestamp.
At the execution layer, the update will then happen in the first produced block after the scheduled timestamp.
For example the \textit{Shanghai} hard fork was scheduled to occur at 2023-04-12 10:27:35 UTC, on Epoch 194,048.
Validators failed to propose a block during the two first slots of this Epoch, but at slot 6,209,538 a validator finally proposed a the block 17,034,870, marking the transition to \textit{Shanghai} on the execution layer.

@@

\linkdest{selfdestruct}{}0xff & {\small SELFDESTRUCT} & 1 & 0 & Halt execution and register account for later deletion. Readers should be warned, \\
&&&& since the \textit{Shanghai} update, this opcode has been marked as deprecated. \\
&&&& Its behavior might be subject to change in an upcoming update. \\
